---
date: "2022-03-16T11:35:01+06:00"
title: Running a multi-MSE
weight: 3
---



```{r echo = FALSE, results='asis'}
library(MSEtool, quietly = TRUE)
library(DLMtool, quietly=TRUE)
openMSE:::makeTOC() 

Stocks <- list(Bluefin_tuna, Herring)

Fleets_both_Stocks <- list(Generic_FlatE, Generic_IncE, Generic_DecE) 
Fleets <- list( Fleets_both_Stocks, # Bluefin (position 1 in Stocks)
                Fleets_both_Stocks) # Herring (position 2 in Stocks)

#                      Fleet 1             Fleet 2          Fleet 3
Bluefin_obs <- list(Precise_Unbiased, Precise_Unbiased, Precise_Unbiased)
Herring_obs <- list(Imprecise_Biased, Imprecise_Biased, Imprecise_Biased)
Obs <- list(Bluefin_obs,    # Bluefin (position 1 in Stocks)
             Herring_obs)    # Herring (position 2 in Stocks)

Imp_both_Stocks <- list(Perfect_Imp, Perfect_Imp, Overages)
Imps <- list( Imp_both_Stocks,   # Bluefin (position 1 in Stocks)
              Imp_both_Stocks)   # Herring (position 2 in Stocks)

nsim = 4
#                  Fleet1  Fleet2   Fleet3
bluefin_catchfrac<-c(0.8,   0.01,   0.19)
herring_catchfrac<-c(0.05,  0.6,    0.35)
CatchFrac <- list(
                  matrix( rep(bluefin_catchfrac, each=nsim), nrow=nsim),
                  matrix( rep(herring_catchfrac, each=nsim), nrow=nsim)
)


ages <- 1:60
bf_M <- mean(Bluefin_tuna@M)          # natural mortality rate
bf_Linf <- mean(Bluefin_tuna@Linf)    # asymptotic length
bf_K <- mean(Bluefin_tuna@K)          # von Bertalanffy growth parameter K
bf_t0 <- mean(Bluefin_tuna@t0)        # von B. theoretical age at length zero
bf_R0 <- Bluefin_tuna@R0              # unfished recruitment

bf_surv <- bf_R0*exp(-bf_M*(ages-1))             # survival
bf_wt_age <- bf_Linf*(1-exp(-bf_K*(ages-bf_t0))) # weight at age   
bf_unfished <- sum(bf_R0*bf_surv*bf_wt_age)      # approxiate estimate of unfished biomass

M_err <- rlnorm(100,0,0.05)
M_2 <- seq(0.2,0.4,length.out=100) * M_err  # made up herring (stock 2) M values
B_1 <- seq(0,bf_unfished,length.out=100)    # made up bluefin tuna abundance levels

dat <- data.frame(M_2,B_1)
bfB_hM <- lm(M_2~B_1,dat=dat) # a linear model predicting M for stock 2 from biomass B for stock 1

Rel <- list(bfB_hM)

MOM_BH <- new('MOM', Stocks, Fleets, Obs, Imps, CatchFrac, Rel = Rel, nsim = nsim)
```

### Running the multi-MSE

Let’s take the fantastical bluefin-herring MOM operating model object (`MOM_BH`) that we created [earlier](/features-multimse/multi-om/) and run a multi MSE for some stock-specific MPs and plot the results:



```{r, cache=TRUE, warning=FALSE}
MPs_BH <- list( c("DCAC", "DBSRA", "AvC", "MCD"),  # Bluefin
                c("DCAC", "DBSRA", "AvC", "MCD"))  # Herring

MMSE_BH <- multiMSE(MOM_BH, MPs=MPs_BH, silent = TRUE)

plot(MMSE_BH)
```

### Understanding the MMSE object

The MMSE object produced from multiMSE has a number of slots. The easiest way to understand these is to interrogate the help documentation:

```{r, eval=FALSE}
class?MMSE
```
