---
date: "2021-03-24T15:18:01+06:00"
title: openMSE Management Procedures
weight: 1
---
 
```{r, include=FALSE}
library(openMSE)
```

There are a large number of management procedures available in the three `openMSE` packages: `MSEtool`, `DLMtool`, and `SAMtool`.

All MPs are available when the `openMSE` package is loaded. 

#### MSEtool MPs

```{r, include=FALSE}
MP <- avail('MP', 'MSEtool')
```

The `MSEtool` package contains `r length(MP)` reference MPs:

```{r}
avail('MP', 'MSEtool')
```

These are indicated by the 'ref' in the MP name. Reference MPs do not have implementation error applied to them, and are typically used as a reference for the management performance that is possible under a range of idealized management scenarios (e.g., fishing exactly at $F_{MSY}$ or some fraction of it).

#### DLMtool MPs
```{r, include=FALSE}
MP <- avail('MP', 'DLMtool')
```

The `DLMtool` package contains `r length(MP)` data-limited MPs:
```{r}
avail('MP', 'DLMtool')
```

The MPs in `DLMtool` are classified as data-limited MPs, as they do not include a stock assessment model, and in most cases do not fit a dynamic model to the fishery data (e.g., MPs are constant management recommendations or iterative index-tracking methods). 

#### SAMtool MPs
```{r, include=FALSE}
MP <- avail('MP', 'SAMtool')
```

The `SAMtool` package contains `r length(MP)` data-moderate and data-rich MPs:

```{r}
avail('MP', 'SAMtool')
```

MPs in the `SAMtool` package include a stock assessment model (class `Assess`) and a harvest control rule (class `HCR`). See the [Stock Assessment Models](/features-assessment-models/) section and the [SAMtool Help Documentation](https://samtool.openmse.com/articles/SAMtool.html) for more information.

