---
date: "2021-02-16T15:18:01+06:00"
title: Spatial & Movement
weight: 7
---

```{r,include=FALSE}
library(openMSE)
printDesc <- function(slot, class="Stock") {
  Desc <- get(paste0(class, "Description"))
  Desc$Description[which(Desc$Slot == slot)]
}
```

The MSEtool uses a two-box spatial model. Users can specify the percent of total habitat and fraction of the population in each area. Life-history characteristics do not vary across the two spatial areas. 

The fleet allocates fishing effort across areas in response to catch rates unless [`Spat_targ`](/object-fleet/4-mpa-targeting/#spat_targ) is used to allow for additional targeting or avoidance behavior, or an area is closed to fishing (see [`Fleet@MPA`](/object-fleet/4-mpa-targeting) or [MPs that create closed areas](/features-management-procedures/)). Movement is parameterized as the probability of an individual staying in a given area for an entire time step.

### Size_area_1
`r printDesc("Size_area_1")`

### Frac_area_1 
`r printDesc("Frac_area_1")`

### Prob_staying
`r printDesc("Prob_staying")`

### Custom Parameters

- more than 2 areas
- spatial closures by year
 

### Interactive App 
Choose upper and lower bounds for Size_area_1, Frac_area_1 and Prob_staying. Based on these ranges, the MSEtool will display  parameter values for 5 simulations in the table. Click on any line of the table to visualize the movement rate for that simulation in the figures below. 

* Figure 1 shows the size and a distribution of the population between area 1 (blue dots) and area 2 (green dots) at a given movement rate over the course of 4 years. The initial population distribution is determined by the values selected for Size_area_1 and Frac_area_1. Users can select years 1, 2, 3 or 4 to visualize how individual fish are likely to move under the selected Prob_staying over multiple time steps.

```{r, echo=FALSE, screenshot.opts = list(delay = 5)} 
knitr::include_app("https://apps.bluematterscience.com/openMSE/stock/spatial",height="850px") 
```

