---
date: "2021-02-18T15:18:01+06:00"
title: Fishing Effort
weight: 2
---

```{r,include=FALSE}
library(openMSE)
printDesc <- function(slot, class="Fleet") {
  Desc <- get(paste0(class, "Description"))
  Desc$Description[which(Desc$Slot == slot)]
}
```

This section includes parameters related to historical and future fishing effort. The MSEtool needs to determine how the fishing mortality rate, which is defined as the proportion of the stock that dies due to fishing, has changed over time. However, in many fisheries, especially those that are data poor, it is easier determine how fishing effort, which can be measured in terms of number of boats, traps, trips, etc., has changed. Fishing effort is related to the fishing mortality rate via the "catchability" parameter (q), and so with some information about historical fishing effort (along with the other information provided) the model is able to infer plausible historical fishing mortality rates. 


The EffUpper and EffLower slots provide a way to include information on how fishing effort changes over the history of the fishery. This information is used to help guide the initialization of the model. When the model is initialized, it samples possible time series of fishing mortality rates and recruitment events that fit the information provided. Series that cannot achieve the specified current depletion level (D) are discarded. 

While historical fishing effort data may be absent in data poor fisheries, there are a number of different types of information that can be used to define EffUpper and EffLower. Information on number of participants or vessels may serve as a proxy if direct effort data (such as number of trips or trawl hours) are not available. Information from older participants may also be used to determine the years during which the fishery first developed, when effort increased, peak effort, and/or effort declines. It is not necessary to include data for every year; the MSEtool will interpolate linearly between the years for which values are provided. While catch can increase or decrease for reasons other than changes in fishing effort, in the absence of effort data catches along with information about participation, market conditions, regulations, etc., may be used to identify historical effort patterns.  

The width of the upper and lower bounds can be used to indicate the level of confidence in the historical effort estimates. More precise effort estimates can be parameterized with smaller ranges between the upper and lower bounds (for example, EffUpper and EffLower are parameterized as +/- 10% of the estimate), while less certain information should have wider bounds to allow the model more freedom in selecting plausible historical fishing mortality rates. In data rich fisheries where estimates of yearly historical fishing mortality rates may be available from a stock assessment, these point values can be provided directly to the model by using the custom parameter `OM@cpars$F_Ind`. If F_Ind is provided there is no need to specify EffLower, EffUpper, and Esd. See the [Custom Parameters]() section for more details.

### EffYears
`r printDesc("EffYears")` 

### EffLower
`r printDesc("EffLower")`  

### EffUpper
`r printDesc("EffUpper")` 

### Esd
`r printDesc("Esd")`

### Custom Parameters
See [Custom Fleet Parameters](/features-custom-parameters/3-fleet/) for information on specifying simulation- and year-specific values for historical fishing effort/mortality.

### Interactive App 
Choose from one of three historical effort patterns. 

Table 1 shows the EffYears, EffUpper, and EffLower values associated with each pattern, and Figure 1 shows the upper and lower bounds on historical fishing effort over time. Then, select upper and lower bounds for the Esd parameter. Table 2 shows randomly drawn parameter values for 5 simulations. Click on any line of the table to view a time series of the yearly relative historical effort selected for that simulation. 

* Figure 1 shows a plot of the upper and lower effort values provided as parameter inputs to help guide model initialization (values also shown in table 1). Note that in this example values are only provided for some years. The graph shows how the MSEtool interpolates between the years for which values are provided in order to guide selection of viable fishing effort values for each simulations.

* Figure 2 shows the time series of historical fishing effort that was selected by the MSEtool during the model initialization phase. Each historical effort trajectory was selected based on the information provided about the upper and lower effort bounds as well as year-to-year variability in effort (Esd), as well as the biological and current depletion parameters. 

<!-- (link to place where model initialization is explained at some point?). -->

```{r, echo=FALSE, screenshot.opts = list(delay = 5)} 
knitr::include_app("https://apps.bluematterscience.com/openMSE/fleet/effort",height="1150px") 
```

