---
date: "2021-03-19T15:18:01+06:00"
title: Implementation of MPs to Control Catch
weight: 2
---

```{r,include=FALSE}
library(openMSE)
printDesc <- function(slot, class="Imp") {
  Desc <- get(paste0(class, "Description"))
  Desc$Description[which(Desc$Slot == slot)]
}
```

This section includes parameters describing the management agency's ability to implement an MP that institutes a catch limit (TAC). For example, an MP may specify a certain TAC, but the managing agency may be unable to stop fishing at the exact moment that the quota is obtained, resulting in quota underages or overages. 

TACFrac and TACSD allow the user to specify the actual catches that are taken as a fraction of the desired TAC in the form of a distribution that allows variability between simulations and years.

### TACFrac
`r printDesc("TACFrac")` 

### TACSD 
`r printDesc("TACSD")`
 

### Custom Parameters
See [Custom Imp Parameters](/features-custom-parameters/5-imp/) for information on specifying simulation- and year-specific implementation error values.

### Interactive App 

```{r, echo=FALSE, screenshot.opts = list(delay = 5)} 
knitr::include_app("https://apps.bluematterscience.com/openMSE/imp/catch",height="750px") 
```

