---
date: "2021-01-19T11:35:01+06:00"
title: Management Procedures
weight: 4
keywords:
  - output controls
  - input controls
  - TAC
---

A key purpose of an MSE is to compare the performance of alternative management approaches, or ***Management Procedures*** to identify the method that is most likely to meet the management objectives for a fishery.

In essence, a Management Procedure is simply a set of rules which define how a fishery will be managed.  These rules can range from simple harvest policies to more complex arrangements.  

For example, a simple Management Procedure may be a constant catch policy, where the annual total allowable catch (TAC) is set a some fixed value.  Alternatively, a more complex Management Procedure may involve multiple data sources, with rules that increase or reduce the TAC in response to trends in one or several indicators.

Management Procedures can differ in data requirements and complexity.  However, all Management Procedures have one thing in common.  They take fishery information and return a management recommendation.

To be included in an MSE, a Management Procedure must be reproducible and able to be coded in a set of instructions.  While fisheries are sometimes managed by expert judgment, it is difficult to reproduce the subjective decision-making process in a computer simulation and include such methods in an MSE.

#### Available Management Procedures

There are over 100 management procedures (MPs) included in the `openMSE` packages. 

The MPs are functions of class `MP` that take an object of class [`Data`](/object-data) and return an object of class [`Rec`](/object-rec) which contains the management recommendation(s).

The first two arguments of an MP are always: 

1. `x` - the simulation number;
2. `Data` - a [`Data object`](/object-data) containing either `OM@nsim` sets of simulated data, or a set of real fishery data (`x` is always one in this case).

The MPs are grouped into two categories:

1. Data-Limited: These MPs are in the `DLMtool` package, and typically use model-free approaches to determine the management recommendations rather than fitting a stock assessment model. More information on the MPs in the `DLMtool` package is available on the [DLMtool documentation page](https://dlmtool.openmse.com);
2. Data-Moderate/Rich: These MPs are in the `SAMtool` package, and are comprised of a stock assessment method linked to a harvest control rule. More information on the MPs in the `SAMtool` package is available on the [SAMtool documentation page](https://samtool.openmse.com);

`openMSE` is extensible, and users can easily develop their own management procedures to use within the framework. Information on this and other details related to the management procedures is available in the [Management Procedure](/features-management-procedures) section.

#### Choosing from the available Management Procedures
```{r, include=FALSE}
library(openMSE)
```

The `avail` function can be used determine which MPs are available. In this case, we are specifying that the `avail` function only search in the `DLMtool` package:

```{r}
allMPs <- avail('MP', 'DLMtool')
```

For the purposes of this quick demonstration, we will select 5 management procedures from the `DLMtool` package and evaluate their 
performance for the operating model we built in the previous section.

```{r}
ourMPs <- allMPs[c(1, 3, 6, 20, 51)] # select 5 MPs
ourMPs
```

Help documentation for the `MP` functions can be accessed in the usual way, e.g., by typing `?AvC` in the console, or by visiting the [DLMtool](https://dlmtool.openmse.com) and [SAMtool](https://samtool.openmse.com) function documentation pages.

In the next section we will run the MSE using these 5 MPs and the OM we constructed in the previous section.

