---
date: "2021-03-23T11:35:01+06:00"
description: Simulated and Real Fishery Data
icon: far fa-table
title: Data Object
type: objects
weight: 7
---

```{r, include=FALSE}
library(openMSE)
```

`Data` is an object class that contains all of the fishery information that can be used by the Management Procedure.  You find the documentation for the `Data` class by typing:

You find the documentation for the `Data` class by typing:
```{r, eval=FALSE}
class?Data
```

You can see from the documentation that the `Data` object, or Fishery Data object, contains many slots, and a lot of information can be stored in this object, including biological parameters, fishery statistics such as time-series of catch, and past management recommendations.

#### In the MSE
In the MSE the Fishery Data object is populated with data that is generated by the simulation model.  Here the 'true' data generated by the model is filtered through the Observation Model (using the [Observation parameters](/object-obs/)) and entered into the Fishery Data object to represent typical fisheries data.

The MSE consists of many hundreds of simulations, and because openMSE has been designed for parallel processing, the Fishery Data object in the MSE actually consists of hundreds of 'versions' of the simulated fishery data. 

The first argument for all [Management Procedure functions](/features-management-procedures/) is `x`, which is the position in the `Data` object that refers to the data corresponding that particular iteration. In the MSE, the value of `x` goes from 1 to the total number of simulations (specificed in `OM@nsim`).

The second argument for all Management Procedures is the `Data` object.

For example, the arguments to the `AvC` MP are:
```{r}
args(AvC)
```

The [Custom Management Procedures section](/features-management-procedures/custommps/) describes the arguments and internal workings of the Management Procedure functions in more detail. 

#### Application of Management Procedures Using Real Fisheries Data 
In contrast to the MSE, in the real world application of a Management Procedure, we only have one version of the fishery data: the data that has been collected from the fishery. 

The Fishery Data object contains all of the fishery information that can be used by a Management Procedure.  By definition, many sources of data are not available in data-limited fisheries, and the Fishery Data object may not be completely populated.  

Functions in `openMSE` can be used to determine which Management Procedures are available to be used given the data in the Fishery Data object, which methods cannot be used, and what data are required to make these methods available. 
See the [Determining Feasible and Available Management Procedures section](/object-data/available/) for more details.




