---
date: "2021-03-22T15:18:01+06:00"
title: Plotting Fleet Object
weight: 6
---

```{r, include=FALSE}
library(openMSE)

```

#### Generate HTML Report
The `plot` function will create a HTML report with plots of the contents of a `Fleet` object. Plotting a `Fleet` object also requires a `Stock` object as the second argument.

For example, running the `plot` function on the example `Generic_DecE` Fleet object:

```{r, eval=FALSE}
plot(Generic_DecE, Albacore)
```

will create [this HTML report](/Generic_Declining_effort_Fleet.html). 

See the [help documentation](https://msetool.openmse.com/reference/plot.Fleet.html) or type `?plot.Fleet` in the R console for more information on plotting `Fleet` objects.

```{r, include=FALSE}
output_dir <- '../../../static/'
plot(Generic_DecE, Albacore, output_dir=output_dir, open=FALSE)
```

#### Plot Stock Components
Individual plots of the components in the `Fleet` object can be generated using the `plot` function and specifying the name of the component to plot in the first argument and a stock object as the second argument. 

The options for plotting the components are shown by clicking the buttons below. 

<div class="nav nav-tabs">
  <button class="tablinks" onclick="openPlot(event, 'Catchability')">Future Catchability</button>
  <button class="tablinks" onclick="openPlot(event, 'Effort')">Historical Effort</button>
  <button class="tablinks" onclick="openPlot(event, 'Selectivity')">Selectivity and Retention</button>
  <button class="tablinks" onclick="openPlot(event, 'MPA')">Historical MPA and Spatial Targeting</button>
</div>

<!-- Tab content -->
<div id="Catchability" class="tabcontent">
```{r}
plot('Catchability', Generic_DecE, Albacore)
```
</div>

<div id="Effort" class="tabcontent">
```{r}
plot('Effort', Generic_DecE, Albacore)
```
</div>


<div id="Selectivity" class="tabcontent">
```{r}
plot('Selectivity', Generic_DecE, Albacore)
```
</div>

<div id="MPA" class="tabcontent">
```{r}
plot('MPA', Generic_DecE, Albacore)
```
</div>
 
Unlike `plot(Fleet, Stock)` which generates a HTML report that opens in the web browser, `plot('character', Fleet, Stock)` will create the plots in the R console. See the [help documentation](https://msetool.openmse.com/reference/plot.Fleet.html) or type `?plot.Fleet` in the R console for more information on plotting `Fleet` objects.
