---
date: "2021-02-22T11:35:01+06:00"
title: Summarizing Management Procedure Performance
weight: 2
---
 
```{r, include=FALSE}
library(openMSE)
MSE <- runMSE(silent=TRUE)
```


### `summary` Table
The `summary` function provides information on the performance of the Management Procedures with respect to the performance metrics. By default, `summary` includes the `PNOF`, `P50`, `AAVY` and `LTY` performance metrics:

```{r}
summary(MSE)
```

It is straightforward to include other `PM` functions by adding the names of the `PM` functions, for example:

```{r}
summary(MSE, 'P100', 'Yield')
```

or all available `PM` functions:
```{r}
summary(MSE, avail('PM'))
```

The `summary` function returns a data frame which can be useful for referring to the PM results elsewhere in the analysis. For example,
```{r}
Results <- summary(MSE, avail('PM'), silent=TRUE) # silent=TRUE to hide print-out to console
Results$Yield # access the PM results


### Trade-Off Plots 

The `TradePlot` function takes an object of class `MSE` and the names of `PM` functions (at least 2) to produce a trade-off plot. For example:

```{r}
TradePlot(MSE) # default plot 
```

The order of the `PM` function names determines plotting on the x and y axes. For example:

```{r}
TradePlot(MSE, 'P50' ,'LTY')  # x = P50, y  = LTY
TradePlot(MSE, 'LTY' ,'P50')  # x = LTY, y = P50
```

The PMs are recycled if an odd number are provided:
```{r}
TradePlot(MSE, 'P50' ,'LTY', 'STY') 
```

The `Lims` argument is used to set the vertical and horizontal acceptable risk thresholds and are interpreted in the same order as the names of the `PM` functions. For example:

```{r}
TradePlot(MSE, 'P50' ,'LTY', Lims=c(0.8, 0))  # 80% minimum acceptable risk for P50, no minimum for LTY
TradePlot(MSE, 'P50' ,'STY', 'P100', 'LTY', Lims=c(0.8, 0, 0.5, 0))  # 80% minimum acceptable risk for P50, 50% for P100, no minimum for STY and LTY
```

```{r include=FALSE}
res <- TradePlot(MSE, 'P50' ,'STY', 'P100', 'LTY', Lims=c(0.8, 0, 0.5, 0), Show=FALSE)
```
The `TradePlot` function returns a data frame with the results of the performance metrics, and a column indicating if an MP has met minimum performance criteria for **all** performance metrics. In the previous example, `r sum(res$Results$Satisificed)` MPs (`r res$Results$MP[res$Results$Satisificed]`) met the minimum performance criteria for all four performance metrics.

The `TradePlot` function can be used to make a variety of custom trade-off plots. For example, the `Tplot`, `Tplot2`, and `Tplot3` functions all use this function to produce different trade-off plots:

```{r}
Tplot
Tplot(MSE)
```

Similarly, we can easily reproduce `NOAA_plot` using the `Tradeplot` function:

```{r}
NOAA_plot(MSE)
TradePlot(MSE, Lims=c(0.5, 0, 0.8, 0.5), 
          PMlist=list("PNOF", "LTY", "P50", "AAVY"), Refs=list(AAVY=0.15))
```
