---
date: "2021-02-22T11:35:01+06:00"
title: Custom Fleet Parameters
weight: 3
---

```{r, include=FALSE}
library(openMSE)
library(dplyr)
cpars <- validcpars(show=FALSE)
```

Simulation specific values for all [Fleet](/object-fleet/) parameters can be set with a vector of length `OM@nsim` in `OM@cpars$SLOT`. 

Some (silly) examples:

```{r, eval=FALSE}
# assuming nsim = 3 
OM@cpars$LFS <- c(100, 200, 300)
OM@cpars$qcv <- c(0.1, 0.2, 0.3)
```

The correlations are maintained when the custom parameters are sampled. See [Generating Correlated Life-History Parameters](/features-custom-parameters/6-correlated-life-history/) for more examples.

```{r, include=FALSE}
printdim <- function(var) {
  tt <- cpars %>% filter(Var.==var)
  tt$Dim[1]
}

```

### Fishing Effort
Simulation and year-specific values for historical fishing effort/mortality can be set with `OM@cpars$Find` with dimensions `r printdim('Find')`.

Note that is `OM@cpars$Find` contains actual apical *F* values (rather than scaled F), `OM@cpars$q <- rep(1,OM@nsim)` will skip the optimization for depletion (not necessary as depletion is simply calculated from the selectivity and pattern in F). 

### Selectivity and Retention
Simulation-, age-, and year- specific selectivity pattern can be set with `OM@cpars$V` with dimensions `r printdim('V')`.

Simulation-, length-, and year- specific selectivity pattern can be set with `OM@cpars$SLarray` with dimensions `r printdim('SLarray')`. Note that you must supply `OM@cpars$CAL_bins` or `OM@cpars$CAL_binsmid` as well.

Simulation-, age-, and year- specific retention pattern can be set with `OM@cpars$retA` with dimensions `r printdim('retA')`.

Simulation-, length-, and year- specific retention pattern can be set with `OM@cpars$retL` with dimensions `r printdim('retL')`. Note that you must supply `OM@cpars$CAL_bins` or `OM@cpars$CAL_binsmid` as well.

Simulation- and year-specific discard ratio can be set with `OM@cpars$DR_y` with dimensions: `r printdim('DR_y')`.

### MPAs and Spatial Closures
Time-varying spatial closures can be modeled with `OM@cpars$MPA` with dimensions `r printdim('MPA')`. 

If more than two areas are modeled, `OM@cpars$mov` must also be specified. See [Spatial & Movement](features-custom-parameters/2-stock/#spatial-movement) for details. 

