---
date: "2021-03-19T15:18:01+06:00"
title: Implementation of MPs to Control Size Limits
weight: 4
---

```{r,include=FALSE}
library(openMSE)
printDesc <- function(slot, class="Imp") {
  Desc <- get(paste0(class, "Description"))
  Desc$Description[which(Desc$Slot == slot)]
}
```

This section includes parameters describing the management agency's ability to implement an MP that institutes an size limit. For example, an MP may specify a certain size limit, but the managing agency may be unable to limit all take of undersized fish. 

SizeLimFrac and SizeLimSD allow the user to specify the actual size of fish retained as a fraction of the desired size limit in the form of a distribution that allows variability between simulations and years. 

### SizeLimFrac
`r printDesc("SizeLimFrac")` 

### SizeLimSD 
`r printDesc("SizeLimSD")`
 
### Custom Parameters
TBD

### Interactive App 

```{r, echo=FALSE, screenshot.opts = list(delay = 5)} 
knitr::include_app("https://apps.bluematterscience.com/openMSE/imp/sizelimit",height="750px") 
```

