---
date: "2021-03-04T15:18:01+06:00"
title: Surveys and Indices of Abundance
weight: 4
---

```{r,include=FALSE}
library(openMSE)
printDesc <- function(slot, class="Obs") {
  Desc <- get(paste0(class, "Description"))
  Desc$Description[which(Desc$Slot == slot)]
}
```

The parameters in this section allow the user to specify observation error and persistent directional bias associated with surveys or other indices of abundance used to monitor changes in stock size over time. 

The "I" parameters indicate an index of abundance, while the "B" parameters indicate a measure of absolute abundance. Users may specify two kinds of sampling error to the simulated data: lognormally distributed observation error, and directional bias. If the MPs you are testing do not require time-series data you can leave these parameters blank. 

### Iobs
`r printDesc("Iobs")` 

### Btobs 
`r printDesc("Btobs")`

### Btbiascv
`r printDesc("Btbiascv")`

### beta
`r printDesc("beta")`

### Custom Parameters
TBD 

### Interactive App

```{r, echo=FALSE, screenshot.opts = list(delay = 5)}
# knitr::include_app("https://apps.bluematterscience.com/openMSE/stock/mortality",height="950px") 
```
