---
date: "2021-02-09T11:35:01+06:00"
title: Creating an OM
weight: 2
---

```{r, include=FALSE}
library(openMSE)
MSEextra()
library(MSEextra)
```

Operating Model objects can be created in several ways.

### Import from Excel
The `XL2OM` function imports an operating model from a correctly formatted Excel workbook.

See [here](/om-data-limited/1-initialize-om/) for details on creating and populating the OM Excel workbook.

Example use of the `XL2OM` function:

```{r, eval=F}
OM <- XL2OM(name='OM.xlsx')
```

### Create in R
OM objects can be created in a R session with `new`.

For example:

```{r}
# An empty OM object
OM <- new('OM')

# An OM populated with Stock, Fleet, Obs, and Imp objects
OM <- new('OM', Albacore, Generic_DecE, Precise_Biased, Overages)
```

See the sections on the [Stock](/object-stock), [Fleet](/object-fleet), [Obs](/object-obs), and [Imp](/object-imp) objects for details on these objects.

### Import a Stock Assessment
openMSE includes functions for importing operating models from the output of several commonly used stock assessment packages. 

See [here](/om-data-rich/) for more details.


### Existing Operating Models
Many existing operating models are available in the [Operating Model Library](/om-library/). The OM Excel files can be downloaded
and imported using `XL2OM` described above.

Additionally, the OMs in the [Operating Model Library](/om-library/) are available in the `MSEextra` package:

```{r, eval=FALSE}
# downloads MSEextra package from GitHub
MSEextra()
# load the MSEextra package
library(MSEextra)
```

The `avail` function can be used to determine the OM objects that are available in the R session:

```{r}
# includes the MSEextra OMs
avail('OM')
```
