---
date: "2021-01-19T11:35:01+06:00"
description: The MSE results
icon: far fa-abacus
title: MSE Object
type: objects
weight: 9 
---

```{r, include=FALSE} 
library(openMSE)
```

Objects of class `MSE` are returned by the `Project` and `runMSE` functions, and contain all of the output from the MSE. In this section we will examine the MSE object in more detail.

First we will run an MSE so that we have an MSE object to work with. We will then briefly examine some of the contents of the MSE object. 

We create an OM based on the Blue Shark stock object and other built-in objects:

```{r}
OM <- new('OM', Blue_shark, Generic_Fleet, Imprecise_Biased, Perfect_Imp, nsim=200)
```

Note that we have increased the number of simulations from the default 48 to 200:
```{r}
OM@nsim
```

Let's choose an arbitrary set of MPs:
```{r}
MPs <- c("Fratio", "DCAC", "Fdem", "DD", "matlenlim") 
```

Set up parallel processing:
```{r, message=FALSE, warning=FALSE}
setup()
```

And run the MSE using parallel processing and save the output to an object called `BSharkMSE`:
```{r, cache=TRUE}
BSharkMSE <- runMSE(OM, MPs, parallel = TRUE)
```

```{r, include=FALSE}
saveRDS(BSharkMSE, "../../../BSharkMSE.rda")
nslots <- length(slotNames(BSharkMSE))
nnames <- length(names(BSharkMSE@OM))
```
The names of the slots in an object of class `MSE` can be displayed using the `slotNames` function:
```{r}
slotNames(BSharkMSE)
```
As you can see, `MSE` objects contain all of the information from the MSE, stored in `r nslots` slots.

The following sub-sections describe the contents of the MSE object.
