---
date: "2021-03-22T15:18:01+06:00"
title: Plotting Stock Object
weight: 9
---

```{r, include=FALSE}
library(openMSE)

```

#### Generate HTML Report
The `plot` function will create a HTML report with plots of the contents of a `Stock` object. For example, running the `plot` function on the example `Albacore` Stock object:

```{r, eval=FALSE}
plot(Albacore)
```

will create [this HTML report](/Albacore_Stock.html). See the [help documentation](https://msetool.openmse.com/reference/plot.Stock.html) or type `?plot.Stock` in the R console for more information on plotting `Stock` objects.

```{r, include=FALSE}
output_dir <- '../../../static/'
plot(Albacore, output_dir=output_dir, open=FALSE)
```


#### Plot Stock Components
Individual plots of the components in the `Stock` object can be generated using the `plot` function and specifying the name of the component to plot in the first argument and a stock object as the second argument. 

The options for plotting the components are shown by clicking the buttons below. 

<div class="nav nav-tabs">
  <button class="tablinks" onclick="openPlot(event, 'Depletion')">Depletion & Discard Mortality</button>
  <button class="tablinks" onclick="openPlot(event, 'Growth')">Growth</button>
  <button class="tablinks" onclick="openPlot(event, 'Maturity')">Maturity</button>
  <button class="tablinks" onclick="openPlot(event, 'Mortality')">Natural Mortality</button>
  <button class="tablinks" onclick="openPlot(event, 'Recruitment')">Recruitment</button>
  <button class="tablinks" onclick="openPlot(event, 'Spatial')">Spatial</button>
</div>

<!-- Tab content -->
<div id="Depletion" class="tabcontent">
```{r}
plot('Depletion', Albacore) 
```
</div>

<div id="Growth" class="tabcontent">
```{r}
plot('Growth', Albacore)
```
</div>

<div id="Maturity" class="tabcontent">
```{r}
plot('Maturity', Albacore)
```
</div>

<div id="Mortality" class="tabcontent">
```{r}
plot('M', Albacore)
```
</div>

<div id="Recruitment" class="tabcontent">
```{r}
plot('Recruitment', Albacore)
```
</div>

<div id="Spatial" class="tabcontent">
```{r}
plot('Spatial', Albacore)
```
</div>

Unlike `plot(Stock)` which generates a HTML report that opens in the web browser, `plot('character', Stock)` will create the plots in the R console. 

See the [help documentation](https://msetool.openmse.com/reference/plot.Stock.html) or type `?plot.Stock` in the R console for more information on plotting `Stock` object.

 
