---
date: "2021-03-19T15:18:01+06:00"
title: Marine Protected Areas and Spatial Targeting
weight: 4
---

```{r,include=FALSE}
library(openMSE)
printDesc <- function(slot, class="Fleet") {
  Desc <- get(paste0(class, "Description"))
  Desc$Description[which(Desc$Slot == slot)]
}
```

The MSEtool allows for some paramterization of spatial differences in fishing. Users can close area 1 to fishing for all years (historical and projected) in area 1 by creating a Marine Protected Area (MPA). 

More complex MPAs, such as those that are not present for all years of the simulation, can be created using custom parameters. Users can also specify spatial targeting or avoidance behavior by the fleet.

### MPA
`r printDesc("MPA")` 

### Spat_targ 
`r printDesc("Spat_targ")`

### Custom Parameters
TBD

Matrix specifying spatial closures for historical years. This parameter is different than creating an MP that closes an area to fishing in future projections. Instead, it allows the user to take into the account of a historical or existing closed area on the current biomass and future MP performance. 

### Interactive App

```{r, echo=FALSE, screenshot.opts = list(delay = 5)} 
knitr::include_app("https://apps.bluematterscience.com/openMSE/fleet/spatial",height="1150px") 
