---
date: "2021-03-25T11:35:01+06:00"
title: Management Strategy Evaluation
weight: 3
---

```{r, include=FALSE}
library(openMSE)
```

We now have examples of the two components and are ready to run the MSE.

The simulations are split into two phase:

1. The spool-up period, where the historical fishery is simulated. See [Simulating Historical Fishery](/tutorial-simulation-dynamics/spool-up/) for details.
1. The projection period, where the historical fishery is projected forward and the management procedures are applied to the simulated fishery. See [Simulating Projection Period](/tutorial-simulation-dynamics/projection/) for details.

The `runMSE` function is used to run the management strategy evaluation:
```{r, eval=FALSE}
MSE <- runMSE(OM, MPs=MPs, silent=TRUE)
```

`runMSE` is a wrapper function for two functions:

1. `Simulate` - simulates the spool-up period and returns an object of [class `Hist`](/object-hist/).
1. `Project` - takes an object of [class `Hist`](/object-hist/) and a set of management procedures, simulates the projection period, and returns an object of [class `MSE`](/object-mse/).

See [Simulation Dynamics](/tutorial-simulation-dynamics/) for more details on all that goes on when using the `runMSE`, `Simulate`, or `Project` functions.

The `runMSE` function returns an object of [class `MSE`](/object-mse/) that contains all of the output from the MSE. This object can be [plotted in various ways](/object-mse/examining/) to summarize the [performance of the MPs](/features-calculating-performance/).
