---
date: "2021-02-09T11:35:01+06:00"
description: Characterization of the fishery
icon: far fa-vector-square
title: Operating Model Object
type: objects
weight: 5
---

```{r, include=FALSE}
library(openMSE)
library(dplyr)
library(knitr)
library(kableExtra)
```

The Operating Model (OM) is the main component of the MSE framework. The OM is used to describe the characteristics of a fishery system and contains all the parameters required to simulate the population and fleet dynamics, the collection of data, and the application of a management procedure (e.g., implement a size regulation, effort control, spatial closure, or catch limit).

An OM is built from four separate objects, each containing a set of parameter values for different aspects of the simulation:

1. [Stock object](/object-stock) - parameters describing the stock dynamics
2. [Fleet object](/object-fleet) - parameters describing the fishing fleet dynamics
3. [Obs object](/object-obs) - parameters describing the observation processes 
4. [Imp object](/object-imp) - parameters describing the management implementation

These objects are described in more detail in their respective pages.

```{r, include=FALSE}
OMSlots <- slotNames('OM')
StockSlots <- slotNames('Stock')
FleetSlots <- slotNames('Fleet')
ObsSlots <- slotNames('Obs')
ImpSlots <- slotNames('Imp')

OM_unique <- c('Name', OMSlots[!OMSlots %in% c(StockSlots, FleetSlots, ObsSlots, ImpSlots)], 'Source')
```
In addition to the information contained in the Stock, Fleet, Obs, and Imp objects, an OM object has `r length(OM_unique)` slots with additional operating model information (see Table below). 

The contents of the first 6 slots and the last slots are self-explanatory. The next section describes the remaining slots for the OM object.

```{r, echo=FALSE, results='asis'}
MSEtool::OMDescription %>% kable('html', row.names = T,
                                 caption="Slots in the OM Object, excluding the Stock, Fleet, Obs, and Imp slots.") %>% 
   kableExtra::kable_styling(full_width = F)
```




