---
date: "2021-03-01T15:18:01+06:00"
title: Maturity
weight: 5
---

```{r,include=FALSE}
library(openMSE)
printDesc <- function(slot, class="Stock") {
  Desc <- get(paste0(class, "Description"))
  Desc$Description[which(Desc$Slot == slot)]
}
```

This section includes maturity parameters. The default parameters assume that maturation is size dependent and follows a logistic probability curve. However, age-based maturity or alternative length-maturity relationships can be specified using custom parameters.

### L50
`r printDesc("L50")`

### L50_95 
`r printDesc("L50_95")`


### Custom Parameters
See [Custom Stock Parameters](/features-custom-parameters/2-stock/) for information on specifying time-varying maturity.

### Interactive App 
Choose upper and lower bounds for L_50 and L50_95. Based on these ranges, the MSEtool will display  parameter values for 5 simulations in the table. Click on any line of the table to view the distribution of values for that simulation in the figures below. 

* Figure 1 shows a logistic maturity function based on the size at 50% and 95% maturity values drawn in each simulation

```{r, echo=FALSE, screenshot.opts = list(delay = 5)} 
knitr::include_app("https://apps.bluematterscience.com/openMSE/stock/maturity",height="850px") 
```
