---
date: "2021-08-20T11:35:01+06:00"
title: Importing MOM from SS3
weight: 1
---


```{r, include=FALSE}
library(openMSE)

SSdir <- 'G:/Shared drives/BM shared/4. Resources/9_SS_examples/Simple_discard'
```

The `SS2MOM` function is used to import an operating model from SS3 output to an `MOM` (multi-operating model) object in `openMSE`. The `MOM` object imports the predicted fishery dynamics for the stock(s) and fleet(s) in the SS3 model and reproduces them in the `openMSE` framework. 

The `SS2MOM` function requires an argument specifying the location of the SS3 output:

```{r, eval=FALSE}
SSdir <- 'C:/SS_examples/Simple_discard'
```

Then `SS2MOM` is used to create the `MOM` object from the SS3 output:
```{r}
MOM <- SS2MOM(SSdir)
```

See [`?SS2MOM`](https://msetool.openmse.com/reference/SS2MOM.html) for details on additional optional arguments for the `SS2MOM` function.

## Simulate Multi-Stock, Multi-Fleet OM

The multi-stock/multi-fleet fishery can be simulated using the `SimulateMOM` function:
```{r, eval=FALSE}
multiHist <- SimulateMOM(MOM)
```


```{r, include=FALSE}
multiHist <- SimulateMOM(MOM, silent=TRUE)
```


## Compare MOM and SS3 Output
The fishery dynamics generated by the `MOM` object can be compared to those predicted by the SS3 output with the `plot_SS2MOM` function:

```{r, eval=FALSE}
plot_SS2MOM(multiHist, SSdir)
```

This function generates a HTML report with plots of stock and fishery dynamics (e.g., numbers, biomass, catch) for each stock and fleet in the `MOM`. For example, the MOM comparison report for the above example is available [here](/SS2MOM/SS2MOM.html).

```{r, include=FALSE}
if (!dir.exists("../../../static/SS2MOM")) dir.create("../../../static/SS2MOM")

plot_SS2MOM(multiHist, SSdir, dir="../../../static/SS2MOM")
```
