---
date: "2020-12-16T15:18:01+06:00"
title: Construct an Operating Model Object
weight: 2
---

```{r, include=FALSE}
library(openMSE)
```

`openMSE` uses an age-structured spatial population dynamics model to simulate the fishery dynamics. The parameters for the operating model are stored in an [OM Object](#OM-object).

The simplest way to build an Operating Model object is to stitch together some of the example objects that are included in `openMSE`: 

```{r}
ourOM <- new('OM', Albacore, Generic_IncE, Imprecise_Unbiased, Perfect_Imp)
```

As you can see, the Operating Model object is made up of four sub-components. Here we are using:

1. `Albacore` - an example [Stock Object](#Stock-object) that contains the biological parameters of a stock based on albacore (*Thunnus alalunga*);
2. `Generic_IncE` - an example [Fleet Object](#Fleet-object) describes a generic fishing fleet with an increasing effort pattern;
3. `Imprecise_Unbiased` - an example [Obs Object](#Obs-object) that describes a generally imprecise but unbiased observation process;
4. `Perfect_Imp` - an example [Imp Object](#Imp-object) that assumes the management recommendations are implemented into the fishery without error.

`ourOM` is now an object of class `OM` containing all the information required to simulate the fishery dynamics. 

can read more about the [OM Object](#OM-object)



[OM Object](#OM-object)

S4 classes

Tests: 


- plot Stock
- plot Fleet
- plot Obs
- plot Imp 
- plot OM



