---
date: "2021-03-24T11:35:01+06:00"
title: Simulate Projection Period
weight: 2
---

```{r, include=FALSE}
library(openMSE)
library(MSEextra)
OM <- MSEextra::Hogfish_PR_NOAA
OM@Eobs <- c(0,0)
OM@Ebiascv <- 0
OM@nsim <- 3
```

The `Project` function takes the [Hist object](/object-hist) returned by the `Simulate` function, projects the fishery system forward in time, and applies the management procedures.

For example:
```{r, eval=FALSE}
MPs <- c('AvC', 'DCAC')
MSE <- Project(Hist, MPs=MPs)
```

As mentioned elsewhere, the `runMSE` function is a wrapper for `Simulate` and `Project`. In other words, this will result in an identical MSE object:

```{r, }
MPs <- c('AvC', 'DCAC')
MSE <- runMSE(OM, MPs=MPs)
```

#### Branched Design
The operating model uses a branched design, where it iteratively applies each [Management Procedure](/features-management-procedures/). This has the advantage that exactly the same process and observation error values are used for each simulation. 

This means the management procedures can be compared on a simulation-by-simulation basis, and any difference in biological or yield outcomes is due only to the properties of the management procedure. 


