---
date: "2021-02-22T11:35:01+06:00"
title: Performance Metrics Methods
weight: 1
---
 
```{r, include=FALSE}
library(openMSE)
```

`openMSE` includes a set of functions, of class `PM`, for calculating Performance Metrics. 

The available `PM` functions (referred to as PMs) can be found using the `avail` function:

```{r}
avail("PM")
```

The PMs are used for summarizing the performance of the management procedures and plotting the results in trade-off plots. 

Here we briefly describe the built-in Performance Metrics functions and demonstrate their use. In the next section we describe how users can develop their own `PM` methods. 

Functions of class `PM` are used on an [objects of class `MSE`](/object-MSE), and return an object of class `PMobj`. Most of the time the `PM` functions are used internally in the `summary` or plotting functions, and it will not be necessary to access the `PMobj` directly. 

To demonstrate the `PM` functions we first run a quick example MSE:

```{r, include=FALSE}
MSE <- runMSE(silent=TRUE)
```

```{r, eval=FALSE}
MSE <- runMSE()
```

### Overview of the `PM` Functions

We will use the `P50` function to demonstrate the `PM` methods. Help documentation on the PM methods can be accessed in the usual way: either `?P50` in the R console or on the [relevant page on the `MSEtool` function documentation site](https://msetool.openmse.com/reference/PerformanceMetric.html).

The `P50` PM method calculates the probability that spawning biomass is above half of the spawning biomass that results in maximum sustainable yield $\left(\text{SB} > 0.5\text{SB}_\text{MSY}\right)$. 

```{r P50int, include=FALSE}
p50 <- P50(MSE)
```

Applying the `P50` function to our `MSE` object results in the following output:
```{r P50}
P50(MSE)
```

We can see that the `PM` function calculated, for the 6 MPs in the `MSE` object, the probability $\text{SB} > 0.5\text{SB}_\text{MSY}$ for all `r MSE@proyears` projection years. 

The `PM` function prints out a summary table of the performance metrics statistics for the first 10 simulations and the last simulation (`r MSE@nsim` in this case) for each MP. The final line shows the overall probability of the performance metric, i.e the average performance across all simulations. 

We will look into this output in a little more detail.

We can see that the first MP is `r MSE@MPs[1]` and the performance statistics for the first and second simulations are `r p50@Prob[1,1]` and `r p50@Prob[2,1]`. How have these values been calculated and what do they mean?

Let's first plot the spawning biomass relative to BMSY for the first two simulations of the `AvC` MP:

```{r}
par(mfrow=c(1,2))
plot(1:MSE@proyears, MSE@SB_SBMSY[1,1,], type='l', 
     xlab="Years", ylab="SB/SBMSY", lwd=2, bty="l", ylim=c(0,2),
     main="MP = 'AvC'; Sim =  1")
abline(h=0.5, lty=3)

plot(1:MSE@proyears, MSE@SB_SBMSY[2,1,], type='l', 
     xlab="Years", ylab='', lwd=2, bty="l", ylim=c(0,2),
     main="MP = 'AvC'; Sim =  2")
abline(h=0.5, lty=3)
```

Now we will calculate fraction of years where spawning biomass is above 0.5 $\text{SB}_\text{MSY}$ for the first and second simulations:

```{r}
mean(MSE@SB_SBMSY[1,1,] > 0.5) # first simulation
mean(MSE@SB_SBMSY[2,1,] > 0.5) # second simulation

# identical to: 
sum(MSE@SB_SBMSY[1,1,] > 0.5)/MSE@proyears
sum(MSE@SB_SBMSY[2,1,] > 0.5)/MSE@proyears
```

Notice how the performance statistics for each simulation correspond with the plot shown above? 

The overall performance is then calculated by the probability over all simulations, i.e for the first MP `r MSE@MPs[1]`:
```{r}
mean(MSE@SB_SBMSY[,1,]>0.5)
```

And for `r MSE@nMPs` MPs:
```{r}
round(apply(MSE@SB_SBMSY >0.5, 2, mean),2)
```
which, reassuringly, is the same as the output of the `P50` function.

### Customizing the `PM` Functions

The `PM` functions allow for very quick calculation of performance metrics. For example, suppose that instead of calculating performance over all projection years, we are only interested in the long-term performance, say over the last 10 years. This can be easily achieved using the `Yrs` argument in the `PM` function:

```{r}
P50(MSE, Yrs=c(41,50))
```

Or the first 10 years:

```{r}
P50(MSE, Yrs=c(1,10))
```

The other biomass Performance Metric functions work in the same way:

```{r}
P10(MSE) # probability SB > 0.1SB_MSY for all years
P100(MSE) # probability SB > SB_MSY for all years
```

Long-term, short-term and overall average yield are calculated using `LTY`, `STY` and `Yield` respectively:

```{r}
LTY(MSE)
STY(MSE)
Yield(MSE)
```

The `PNOF` PM function calculates the probability of not overfishing:
```{r }
PNOF(MSE)
```


Finally, the average annual variability in yield (AAVY) can be calculated with the `AAVY` function:

```{r}
AAVY(MSE)
```

By default the `AAVY` PM function calculates the probability that AAVY is less than 20%. This reference level can easily be modified using the `Ref` argument:

```{r}
AAVY(MSE, Ref=0.15) # prob. AAVY < 15%
AAVY(MSE, Ref=0.30) # prob. AAVY < 30%
```

The other `PM` functions also have the `Ref` argument which can be used in the same way. For example, you may notice that the `P50` and `P100` functions are identical except for the value of the `Ref` argument:

```{r}
args(P50)
args(P100)
```

It follows then that it is very simple to calculate a custom performance metric based on the built-in `PM` functions. For example, suppose we wanted to calculate the probability that spawning biomass was above 5% of BMSY. This can be achieved by using any of the biomass-based `PM` functions and modifying the `Ref` argument:

```{r}
P50(MSE, Ref=0.05)
P100(MSE, Ref=0.05)
```

More information on customizing `PM` functions can be found in the [Custom Performance Metrics](../custom-performance-metrics) section.

