---
date: "2021-03-23T15:18:01+06:00"
title: Determining Available MPs
weight: 2
---

```{r, include=FALSE}
library(openMSE)
```
 
Although all management procedures can be tested in the simulation, it is often the case that not all MPs can actually be applied in a fishery. This can happen for two reasons:

1. Insufficient data exists to use an MP, for example, a MP may use catch-at-age data which does not exist for the fishery
2. Management constraints such as issues with enforcement or legal requirements may mean some management options are not possible.

Management procedures which can be applied given the current fishery data are referred to as *Available*. 

Management procedures that return management recommendations that are, at least in theory, applicable to the fishery are referred to as *Feasible*.

openMSE has functions to identify MPs that are *Available* and *Feasible*, and also provides information for what additional data are required to allow *Not Available* MPs to be used.

## Feasible MPs
The `Fease` function can be used to determine which MPs are *Feasible*. 

For example, if only TAC management is feasible in a fishery, the feasible MPs are:
```{r}
Fease(TAC=TRUE, TAE=FALSE, SL=FALSE, Spatial=FALSE)
```

We can confirm that all of these MPs are output controls (return a TAC) by using the `MPtype` function:
```{r}
feaseMPs <- Fease(TAC=TRUE, TAE=FALSE, SL=FALSE, Spatial=FALSE)
MPtype(feaseMPs)
```

If a `Data` object is provided to `Fease`, the function will return the names of MPs that are both feasible in terms of management methods, and available in terms of the fishery data:
```{r}
feaseMPs <- Fease(Atlantic_mackerel, TAC=FALSE, TAE=TRUE, SL=TRUE, Spatial=FALSE, 
                  msg=FALSE)
MPtype(feaseMPs)
```


## Available MPs
The `Can` function generates a list of the MPs that are available to be applied to the Data object:
```{r Can}
Can(Atlantic_mackerel, silent=TRUE)
```

If all management methods are feasible, the list of MPs returned by the `Can` function will be the same as those returned by the `Fease` function when the `Data` object is provided.

## Unavailable MPs
The `Cant` function displays a list of the MPs that cannot be applied to the Data object together with the reason why:
```{r Cant}
Cant(Atlantic_mackerel, silent=TRUE)
```

