---
date: "2021-02-18T15:18:01+06:00"
title: Selectivity and Retention
weight: 3
---

```{r,include=FALSE}
library(openMSE)
printDesc <- function(slot, class="Fleet") {
  Desc <- get(paste0(class, "Description"))
  Desc$Description[which(Desc$Slot == slot)]
}
```

Selectivity is defined as the size or age at which fish are vulnerable to the fishing gear used, and is usually influenced by gear specifications. Retention is defined as the size or age of the fish that are actually kept by the fleet, and usually reflects either management regulations or market preferences. Those fish that are selected but not retained are discarded, and are subject to the [discard mortality rate (`Fdisc`)](/object-stock/2-natural-mortality/#fdisc). 

The MSEtool can model either logistic or dome-shaped selectivity and retention curves. The parameters below specify a single selection and retention curve in terms of lengths for the entire simulation period (unless changed by an MP), but time varying or age-based selection and retention can be specified using custom parameters.

### L5
`r printDesc("L5")` 

### LFS 
`r printDesc("LFS")`
 
### Vmaxlen
`r printDesc("Vmaxlen")`

### isRel
`r printDesc("isRel")`

### LR5
`r printDesc("LR5")`

### LFR
`r printDesc("LFR")`

### Rmaxlen
`r printDesc("Rmaxlen")`

### DR
`r printDesc("DR")`

### Custom Parameters
See [Custom Fleet Parameters](/features-custom-parameters/3-fleet/) for information on specifying simulation- year- and age/length-specific selectivity and retention.

### Interactive App 
Choose upper and lower bounds for each of the 7 selectivity parameters. Based on these ranges, the MSEtool will display  parameter values for 5 simulations in the table. Click on any line of the table to view the the probability that a fish of a given size is selected by the gear, retained if selected, landed, or killed by the gear for that simulation.

* Figure 1 shows the probability that a fish of a given length is selected, retained, or discarded by the fleet. The black line shows the probability that a fish is selected by the fishing gear (black). Small fish may be able to escape through large mesh or escape ports and thus have a very low probability of being vulnerable to the fishing gear, while in other situations (when Vmax is less than 1 and selection probability is dome-shaped) larger fish may be able to evade the fishing gear. The blue line represents the size of fish that are able to be retained by the fleet if selected by the gear. This represents regulations that restrict the size or age of what can be kept. If a fish is selected by the gear, the green line is the probability that it is landed and not discarded at sea (which can happen due to market preference, for example). The yellow line shows the probability that a fish of a given size is killed (removed from the simulated population), whether it is kept or discarded.

```{r, echo=FALSE, screenshot.opts = list(delay = 5)} 
knitr::include_app("https://apps.bluematterscience.com/openMSE/fleet/selectivity",height="1150px") 
```

