---
date: "2021-03-24T11:35:01+06:00"
title: Evaluating an OM
weight: 6
---

```{r, include=FALSE}
library(openMSE)
```

The `Turing` function has been designed to evaluate an Operating Model against a [Data object](/object-data/) from the same fishery. The function generates 5 random samples of Data from the `OM` object and plots these together with the corresponding data in the `Data` object. 

Ideally, in a well conditioned OM one should not be able to visually detect which of the plots are the real data and which have been artificially generated by the operating model.

The `Turing` function takes an object of class `OM` and an object of class `Data`. It first plots the simulated and real data and then waits for user input before revelaing which of the plots are the real data from the `Data` object.  

We use the `wait=FALSE` argument here so that each plot is printed without waiting for user input. 

In this example we are using a `Data` object that was simulated using the same `OM`, so it shouldn't be surprising that it is difficult to detect which of the plots are from the `Data` object (we haven't included the plots here):

```{r eval=FALSE}
Turing(testOM, SimulatedData)
```

The `Turing` function is useful for evaluating if your OM adequately produces fishery data that appears similar (e.g as variable) as your real observed data. See `?Turing` or [function help documentation](https://msetool.openmse.com/reference/Turing.html) for more information.
