---
date: "2021-01-19T11:35:01+06:00"
description: Conditioning the observation model
icon: fas fa-wrench
title: Conditioning OMs with Data
type: features
weight: 5
---

```{r, include=FALSE}
library(openMSE)
```

In this section we demonstrate how the [Observation model](/object-obs) in an operating model can be conditioned with real data.

For conditioning the population dynamics in the operating model, see the [Rapid Conditioning Model]().

#### Create Example OM and Real Data
First we create an operating model using example [Stock](/object-stock/8-example-stock-objects/_index_en/), [Fleet](/object-fleet/example-objects/_index_en/), [Obs](/object-obs/example-objects/_index_en/), and [Imp](/object-imp/example-objects/_index_en/) objects. As it's only an example, we will set only 4 simulations:

```{r}
OM <- new('OM', Albacore, Generic_IncE, Generic_Obs, Perfect_Imp, nsim=4)
```

Then we create an example of our 'real' fishery data (in this case data simulated from a different OM):
```{r}
RealData <- SimulatedData
```
