---
date: "2021-02-20T11:35:01+06:00"
description: Information from the spool-up period
icon: far fa-chart-line
title: Hist Object
type: objects
weight: 6
---

```{r, include=FALSE}
library(openMSE)
```

Objects of class `Hist` contain all of the information from the spool up period. 


#### Creating a `Hist` object 
They are created by running the simulations for only the historical period using the `Simulate` function, for example:

```{r}
OM <- new("OM", Albacore, Generic_IncE, Imprecise_Biased, Perfect_Imp)
myHist <- Simulate(OM, silent=TRUE)
class(myHist)
```

The `Hist` object contains all of the information from the historical spool-up period. This information will be used when the model is run in projection mode.

See the [Hist slots](1-contents) page for more details on the information stored in the `Hist` object.

#### Plotting a `Hist` object
The simulated dynamics for the historical spool-up period can be examined by plotting the `Hist` object:

```{r, eval=FALSE}
plot(myHist)
```

The `plot` function creates an HTML report with plots of the sampled OM parameters and the dynamics of the historical spool-up period.

#### Historical data
The first slot in the `Hist` object is an object of class `Data`. This is the [`Data` object](/object-data/) that was created at the end of the spool-up period, and will be used in the first year of the projection period. 

Running an MP on `Hist@Data` will result in identical management recommendations as those in the first year of the projection period using the same `OM`. 


#### Running the projections
The projections can be run directly from a `Hist` object using the `Project` function:

```{r}
myMSE <- Project(myHist, MPs=c("AvC", "FMSYref", "Itarget1"))
```

Note that the `runMSE` function is a wrapper for `Simulate` and `Projects`, and:

```{r, eval=FALSE}
myMSE <- runMSE(OM, MPs=c("AvC", "FMSYref", "Itarget1"))
```

would result in an identical [`MSE` object](/object-mse).

