---
date: "2021-01-19T11:35:01+06:00"
description: Output from Management Procedures
icon: far fa-arrows
title: Rec Object
type: objects
weight: 8
---

```{r, include=FALSE}
library(openMSE)
```

[Management Procedures](/features-management-procedures/) return S4 objects of class `Rec` containing the management recommendations returned by an MP.

`Rec` objects have the following slots:
```{r}
slotNames('Rec')
```

Information on the contents the `Rec` object is available in the [help documentation](https://msetool.openmse.com/reference/Rec-class.html) or by typing `class?Rec` in the R console.


We demonstrate the `Rec` object by applying several management procedures of different types to the `Cobia` [example Data object](/object-data/example/).

First, we use the `Can` function to determine which [MPs can be run](/features-management-procedures/available/) on the `Cobia` data:

```{r}
MPs <- Can(Cobia, silent=TRUE)
MPtype(MPs)
```

Next we [apply several MPs](/features-management-procedures/running/) in turn to the `Cobia` data.

#### Effort Control MP

Apply `ItargetE1` MP to `Cobia`:
```{r}
Rec <- ItargetE1(1, Cobia)
class(Rec)
Rec
```

The MP returns an object of class `Rec`. By default, printing the `Rec` object to the console will only show the slots that are populated, in this case the `Effort` slot is the only slot that has been populated by the MP:

```{r}
Rec@Effort
Rec@TAC
```

#### Size Limit MP 

Apply `matlenlim` MP which sets the length-at-retention to the length-at-maturity:

```{r}
Rec <- matlenlim(1, Cobia)
Rec
```

#### Catch Limit MP 

Apply `AvC` MP which sets the TAC to the average historical catch:
```{r}
Rec <- AvC(1, Cobia, reps=1000) 
Rec
```

Note that the `TAC` slot contains 1000 `reps` of the average catch (assuming a CV of 0.2, see `?AvC` for details):

```{r}
length(Rec@TAC)
hist(Rec@TAC)
```
Printing the `Rec` object returns the median of the 1000 `reps`:

```{r}
Rec
```


#### Mixed MP (TAC and Spatial)
Apply `Itarget1_MPA` MP which sets a TAC and closes Area 1:

```{r}
Rec <- Itarget1_MPA(1, Cobia, reps=1000) 
Rec
```
