---
date: "2021-02-22T11:35:01+06:00"
title: Custom Stock Parameters
weight: 2
---

```{r, include=FALSE}
library(openMSE)
library(dplyr)
cpars <- validcpars(show=FALSE)
```

Simulation specific values for all [Stock](/object-stock/) parameters can be set with a vector of length `OM@nsim` in `OM@cpars$SLOT`. 

Some (silly) examples:

```{r, eval=FALSE}
# assuming nsim = 3 
OM@cpars$M <- c(0.1, 0.2, 0.3)
OM@cpars$Linf <- c(100, 200, 300)
OM@cpars$K <- c(0.3, 0.2, 0.1)
```

The correlations are maintained when the custom parameters are sampled. See [Generating Correlated Life-History Parameters](/features-custom-parameters/6-correlated-life-history/) for more examples.

```{r, include=FALSE}
printdim <- function(var) {
  tt <- cpars %>% filter(Var.==var)
  tt$Dim
}

```

### Natural Mortality
For simulation-, age- and year-specific values, use `OM@cpars$M_ageArray` with dimensions: `r printdim('M_ageArray')`.

### Discard Mortality
For simulation-, age- and year-specific discard mortality  use `OM@cpars$Fdisc_array1` with dimensions: `r printdim('Fdisc_array1')`.

For simulation-, length- and year-specific discard mortality  use `OM@cpars$Fdisc_array2` with dimensions: `r printdim('Fdisc_array2')`. Note that you must supply `OM@cpars$CAL_bins` or `OM@cpars$CAL_binsmid` as well.

### Virgin Recruitment (R0)
By default `OM@R0` is a single value that applies to all simulations.

Simulation-specific values for R0 can be set with `OM@cpars$R0`, e.g., `OM@cpars$R0 <- c(1000, 2000, 1000)`.

### Recruitment Deviations
For simulation- and year-specific recruitment deviations, use `OM@cpars$Perr_y` with dimensions: `r printdim('Perr_y')`. 

The first `maxage` values are the recruitment deviations for the age-classes in the initial year.

Note that when `OM@cpars$Perr_y` is populated, `OM@Perr` and `OM@AC` are ignored.

### Size-at-Age
For simulation-, age- and year-specific values for mean length-at-age, use `OM@cpars$Len_age` with dimensions: `r printdim('Len_age')`.

For simulation-, age- and year-specific values for standard deviation of length-at-age, use `OM@cpars$LatASD` with dimensions: `r printdim('LatASD')`.

For simulation-, age- and year-specific values for mean weight-at-age, use `OM@cpars$Wt_age` with dimensions: `r printdim('Wt_age')`.

### Maturity-at-Age
For simulation-, age- and year-specific values for maturity-at-age, use `OM@cpars$Mat_age` with dimensions: `r printdim('Mat_age')`.


### Depletion & Initial Depletion
Simulation specific values for depletion can be set as a numeric vector of length `OM@nsim` in `OM@cpars$D`.

[Initial depletion](/tutorial-reference-points/initial_depletion/) (depletion in first year) can be set with `OM@cpars$initD`.

### Spatial & Movement
Custom movement matrix can be included with `OM@cpars$mov` with dimensions: `r printdim('mov')`. 

Custom area size (for more than 2 areas) can be set with `OM@cpars$Asize`  with dimensions: `r printdim('Asize')`. 

