---
date: "2021-03-238T15:18:01+06:00"
title: Creating Data Input Files
weight: 1
---

```{r, include=FALSE}
library(openMSE)
```

```{r, include=FALSE}
if (!dir.exists("../../../static/ExampleData")) dir.create("../../../static/ExampleData")
DataInit("MyData", dir="../../../static/ExampleData", overwrite = TRUE)
```
Probably the easiest way to get your data into `openMSE` is to populate a data table in an Excel workbook. 

You can create a Data workbook using the `DataInit` function, for example:
```{r, eval=FALSE}
DataInit("MyData")
```

This will create two files in your current working directory: 'MyData.xlsx' and 'MyData.md'.

#### Excel Data Input File
The Excel data input file is a standardized file format for fishery data that uses a standardized spreadsheet format: either a CSV (comma separated file; file extension .csv') or a MS Excel file (file extension .xlsx or .xls). Support for Google Sheets may be added later. 

You do not have to enter data for every line of the data file, if data are not available simply put an 'NA' next to any given field. See the [Populating the Fishery Object section](/tutorial-populating-data/) for more details.

#### Markdown Documentation File
The Data Documentation file is a companion document that contains supporting information for the quantitative data in the input file. For example, the data documentation file can include a written description of the sources of the various data, the methods used to obtain the data, and relevant references to data sources or other information relating to the data preparation.

The Data Documentation file can be opened in any ordinary text editor (e.g., Notepad, Wordpad, or MS Word). It must be saved as an ordinary text file with extension '.md' (i.e., do not save as '.doc' or '.docx').

We suggest having the Data Input and Data Documentation files both open and documenting the data sources in the Documentation file while entering the quantitative data in the Input file.

The Data Documentation file uses the Markdown text formatting syntax. This means that all entries should be plain text. Markdown is very powerful, and it is straightforward to include additional formatting such as equations, bullet points, or ordered lists. See the [Markdown cheat sheet](https://guides.github.com/pdfs/markdown-cheatsheet-online.pdf) for more information.

It is not necessary to be familiar with Markdown to enter information in the Data Documentation file. The main thing to be aware of is that headings are indicated with the # symbol; for example '#' is a first level heading, '##' is a second level heading, and so on.

See the [Populating the Fishery Object section](/tutorial-populating-data/) for more details on populating the Data Documentation File.

The Fishery Data can be combined with the Data Documentation file to generate a [report of the Data object](/object-data/plotting/#data-report). 
