---
date: "2021-02-22T11:35:01+06:00"
title: Custom Obs Parameters
weight: 4
---

```{r, include=FALSE}
library(openMSE)
library(dplyr)
cpars <- validcpars(show=FALSE)
```

Simulation specific values for all [Obs](/object-obs/) parameters can be set with a vector of length `OM@nsim` in `OM@cpars$SLOT`. 

The correlations are maintained when the custom parameters are sampled. See [Generating Correlated Life-History Parameters](/features-custom-parameters/6-correlated-life-history/) for more examples.

```{r, include=FALSE}
printdim <- function(var) {
  tt <- cpars %>% filter(Var.==var)
  tt$Dim[1]
}

```

### Catch Observations
Simulation and year-specific values for catch observation error can be added with `OM@cpars$Cobs_y` with dimensions `r printdim('Cobs_y')`.

### Effort Observations
Simulation and year-specific values for catch observation error can be added with `OM@cpars$Eobs_y` with dimensions `r printdim('Eobs_y')`.

### Biological Sampling
Simulation specific sampling bias for observed biological parameters can be as a vector of length `OM@nsim` with:

* `OM@cpars$LenMbias`
* `OM@cpars$Mbias`
* `OM@cpars$Kbias`
* `OM@cpars$t0bias`
* `OM@cpars$Linfbias`
* `OM@cpars$LFCbias`
* `OM@cpars$LFSbias`

Time-varying sampling bias is not possible at this stage.

To set simulation specific values for the observed steepness, use `OM@cpars$hsim` as a vector of length `OM@nsim` with the assumed steepness values.

### Surveys and Indices
Simulation and year-specific values for observation error for index of total biomass be added with `OM@cpars$Ierr_y` with dimensions `r printdim('Ierr_y')`.

Simulation and year-specific values for observation error for index of spawning biomass be added with `OM@cpars$SpIerr_y` with dimensions `r printdim('SpIerr_y')`.

Simulation and year-specific values for observation error for index of vulnerable biomass be added with `OM@cpars$VIerr_y` with dimensions `r printdim('VIerr_y')`.

Simulation specific values for hyperstability/depletion parameter (beta) for index of total biomass be added with `OM@cpars$I_beta` with dimensions `r printdim('I_beta')`.

Simulation specific values for hyperstability/depletion parameter (beta) for index of spawning biomass be added with `OM@cpars$SpI_beta` with dimensions `r printdim('SpI_beta')`.

Simulation specific values for hyperstability/depletion parameter (beta)  for index of vulnerable biomass be added with `OM@cpars$VI_beta` with dimensions `r printdim('VI_beta')`.

Simulation and year-specific values for observed abundance be added with `OM@cpars$Aerr_y` with dimensions `r printdim('Aerr_y')`.

### Reference Points
Simulation specific sampling bias for observed reference points can be as a vector of length `OM@nsim` with:

* `OM@cpars$FMSY_M`
* `OM@cpars$BMSY_B0`
* `OM@cpars$Irefbias`
* `OM@cpars$Crefbias`
* `OM@cpars$Brefbias`
* `OM@cpars$Dbias`
* `OM@cpars$hbias`
* `OM@cpars$Recbias`
* `OM@cpars$sigmaRbias`

Time-varying sampling bias is not possible at this stage.



