---
date: "2021-02-22T11:35:01+06:00"
title: Custom Imp Parameters
weight: 5
---


```{r, include=FALSE}
library(openMSE)
library(dplyr)
cpars <- validcpars(show=FALSE)
```

Simulation specific values for all [Imp](/object-fleet/) parameters can be set with a vector of length `OM@nsim` in `OM@cpars$SLOT`. 

The correlations are maintained when the custom parameters are sampled. See [Generating Correlated Life-History Parameters](/features-custom-parameters/6-correlated-life-history/) for more examples.

```{r, include=FALSE}
printdim <- function(var) {
  tt <- cpars %>% filter(Var.==var)
  tt$Dim[1]
}

```

### TAC Implementation Error
Simulation and year-specific values for implementation error in TAC can be set with `OM@cpars$TAC_y` with dimensions `r printdim('TAC_y')`.

### TAE Implementation Error
Simulation and year-specific values for implementation error in TAC can be set with `OM@cpars$E_y` with dimensions `r printdim('E_y')`.

### Size Limit Implementation Error
Simulation and year-specific values for implementation error in TAC can be set with `OM@cpars$SizeLim_y` with dimensions `r printdim('SizeLim_y')`.
