---
date: "2021-03-19T15:18:01+06:00"
title: Implementation of MPs to Control Effort
weight: 3
---

```{r,include=FALSE}
library(openMSE)
printDesc <- function(slot, class="Imp") {
  Desc <- get(paste0(class, "Description"))
  Desc$Description[which(Desc$Slot == slot)]
}
```

This section includes parameters describing the management agency's ability to implement an MP that institutes an effort limit (TAE). For example, an MP may specify a certain TAE, but the managing agency may be unable to stop fishing at the exact moment that the effort limit is reached, resulting in underages or overages. 

TAEFrac and TAESD allow the user to specify the actual effort employed as a fraction of the desired TAE in the form of a distribution that allows variability between simulations and years. 

### TAEFrac
`r printDesc("TAEFrac")` 

### TAESD 
`r printDesc("TAESD")`
 

### Custom Parameters
See [Custom Imp Parameters](/features-custom-parameters/5-imp/) for information on specifying simulation- and year-specific implementation error values.

### Interactive App 
Choose upper and lower bounds for `TAEFrac` and `TAESD.` Based on these ranges, the parameter values for 5 simulations will show in the table. Click on any line of the table to view how those parameter values affect the implemented vs. desired TAE in a hypothetical situation where the MP modeled recommends a decline in TAE over time.

* Figure 1 shows the effects of implementation error in the recommended TAE over 50 projection years in a single simulation. The red line shows the TAE recommended by the MP, while the blue line shows the actual effort limit applied by the model. The location of the blue line relative to the red line is influenced by whether `TAEFrac` is greater or less than 1, and the variability of the blue line over time is influenced by the value of `TAESD`, with larger values resulting in greater variation between years.

```{r, echo=FALSE, screenshot.opts = list(delay = 5)} 
knitr::include_app("https://apps.bluematterscience.com/openMSE/imp/effort",height="750px") 
```

