---
date: "2021-03-23T15:18:01+06:00"
title: Applying Management Procedures
weight: 3
---
 
```{r, include=FALSE}
library(openMSE)
```

The `runMP` function can be used to apply a MP to a Data object. For example, to apply the `AvC` method:
```{r}
runMP(Atlantic_mackerel, "AvC", reps=1000)
```

The `runMP` prints out the MP recommendations to the console. In the case of a TAC, where multiple repititions where (see `reps` = 1000 above) used the `runMP` function prints the median TAC recommendation.

Although it only displays a summary, `runMP` invisibly returns the Data object with the TAC slot populated:

```{r}
Recs <- runMP(Atlantic_mackerel, "AvC")
hist(Recs@TAC)
```

`runMP` can be used to run several MPs:
```{r}
runMP(Atlantic_mackerel, c("AvC", "AvC_MLL"))
```

Or all available MPs:
```{r}
Atlantic_mackerel <- runMP(Atlantic_mackerel, reps=1000, chkMPs=TRUE, silent=TRUE)
```

The TAC recommendations from each Output control can be plotted:

```{r, fig.height=7, fig.width=6}
boxplot(Atlantic_mackerel)
```


