---
date: "2021-01-21T11:35:01+06:00"
title: Management Strategy Evaluation
weight: 5
---

```{r, include=FALSE}
library(openMSE)
ourMPs <- c("AvC", "BK", "CC1", "DCAC","Islope1") 
ourOM <- new('OM', Albacore, Generic_IncE, Imprecise_Unbiased, Perfect_Imp)
```

Now that we have an operating model and a set of management procedures, we are ready to run our first management strategy evaluation.

The MSE is run with the `runMSE` function, which requires two arguments: a `OM` object (`ourOM` in this case) and a character vector with the names of the MPs that will be tested (`ourMPs`):

```{r, cache=TRUE}
MSE <- runMSE(OM=ourOM, MPs=ourMPs)
```

```{r, include=FALSE}
saveRDS(MSE, "../../../objects/walkthroughMSE.rda")
```

The `runMSE` function first runs the historical simulations (the spool-up period) and then runs the MSE for the specified MPs. Messages are printed in the console to show the progress. 

The `runMSE` function returns an object of class `MSE`, an S4 object with all of the information from the MSE run.

For example, the slot `SB_SBMSY` is a 3-dimensional array with the spawning biomass ($\text{SB}$) relative to the spawning biomass corresponding to maximum sustainable yield ($\text{SB}_{\text{MSY}}$; see [Reference Points](/tutorial-reference_points/) for more details) for each simulation, MP, and projection year:

```{r}
class(MSE@SB_SBMSY)
dim(MSE@SB_SBMSY)
```

See the [Running the MSE](/features-running-mse/) and the [`MSE` object](/object-mse/) pages for more details.

In the next section we will examine the MSE results. 
