---
date: "2021-03-23T15:18:01+06:00"
title: Conditioning with Life-History Information
weight: 5
---

```{r, include=FALSE}
library(openMSE)
OM <- new('OM', Albacore, Generic_IncE, Generic_Obs, Perfect_Imp, nsim=4)
RealData <- SimulatedData

printDesc <- function(slot, class="Data") {
  Desc <- get(paste0(class, "Description"))
  Desc$Description[which(Desc$Slot == slot)]
}
```

By default, the life-history information provided to the [Management Procedures](/features-management-procedures/) is determined by the real life-history values specified in the OM (e.g., `OM@Linf`) and the [bias specified in the observation model](/object-obs/biological_sampling/). 

For example:

```{r}
OM <- new('OM', Albacore, Generic_IncE, Generic_Obs, Perfect_Imp, nsim=4)
Hist <- Simulate(OM, silent=TRUE)

# OM Linf values in last historical year
Hist@SampPars$Stock$Linfarray[,OM@nyears]

# Linf values provided to MP in this year (ie in simulated Data)
Hist@Data@vbLinf

# Observation error applied to OM values
Hist@SampPars$Stock$Linfarray[,OM@nyears] * Hist@SampPars$Obs$Linfbias
```

Users can provide specific values for the life-history parameters by including them in the Data object. We demonstrate here with `Linf`, but the same concept applies for all life-history parameters (`M`, `K`, `L50`, etc).

#### Add Life-History Data to OM

Create a blank [Data object](/object-data):
```{r}
Data <- new('Data')
```

Add our 'observed` values for `Linf` - i.e., the values we wish to provide to the MPs:
```{r}
Data@vbLinf <- 100
```

Add `Data` to `OM`:
```{r}
OM@cpars$Data <- Data
```

Simulate the [spool-up period](/tutorial-simulation-dynamics/spool-up/) (now with Data included in the OM):
```{r}
Hist <- Simulate(OM, silent=TRUE)
```

Our 'observed' life-history parameters are now provided to the MPs:
```{r}
Hist@Data@vbLinf
```

Similar to conditioning with other data, when real life-history values are provided in the `Data` object, the observation parameters (e.g., `Obs@Linfbiascv`) are ignored.

