---
draft: false
title: Operating Model Library
---

<link rel="stylesheet" type="text/css" href="http://cdn.datatables.net/1.10.5/css/jquery.dataTables.min.css">
<script src="http://code.jquery.com/jquery-2.1.2.min.js"></script>
<script src="http://cdn.datatables.net/1.10.5/js/jquery.dataTables.min.js"></script>

<script type="text/javascript">
         $(document).ready(function() {
             $("table").DataTable({
               "aLengthMenu": [[50, 75, 100, -1], [50, 75, 100, "All"]],
               "iDisplayLength": 75
             });
         } );
         
</script>

The Operating Model library contains complete OM reports and corresponding OM Excel and R input files for a growing number of fisheries.

Each report uses a standardized format that can be generated from within `openMSE`.  

We will be adding operating models over time, with the goal of including the broadest range of fisheries to which the `openMSE` packages have been applied.  The standardized format is intended to provide a readily available resource for the development of new operating models for additional fisheries over time.  We are also developing a standardized MSE report, which will be added to the library of fisheries soon.  Please [contact us](/contact) if you’d like to include an operating model in the library.


```{r include=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)

DF <- readRDS("../../../MSEextra/build_package/DF.rda")

DF <- DF %>% 
  mutate('OM R Data'=paste0("<a href='", DF$OMpathout,"'> Link</a>")) %>% 
  mutate('OM Excel'=paste0("<a href='", DF$OM.XL,"'download> Link</a>")) %>% 
  mutate('OM Report'=paste0("<a href='", DF$OM.Report,"'target='_blank' download> Link</a>")) %>%
  mutate('MSE Report'=paste0("<a href='", DF$MSE.Report,"'download> Link</a>")) 

ind <- !DF$hasOMrep
if (sum(ind)>0) DF['OM Report'][ind,1] <- ''

ind <- !DF$hasOMxl
if (sum(ind)>0) DF['OM Excel'][ind,1] <- ''


ind <- !DF$hasMSErep
if (sum(ind)>0) DF['MSE Report'][ind,1] <- ''

DFout <- DF %>% select(Name, Species, Region, Agency, 'OM Report', 'MSE Report', 'OM Excel', 'OM R Data', Class, Family) 

# htmlTable::htmlTable(DFout, css.cell = "padding-left: 1em; padding-right: 1em;", align = "rrrr")

Table <- DFout %>% kable("html", escape=F,  table.attr = "class='dtable'", align="llllcccclll") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, position="float_left", font_size = 14) %>%
  kableExtra::column_spec(1) %>%
  kableExtra::column_spec(2, italic=TRUE) %>%
  kableExtra::column_spec(3) %>%
  kableExtra::column_spec(4) %>%
  kableExtra::column_spec(5) %>%
  kableExtra::column_spec(6) %>%
  kableExtra::column_spec(7) %>%
  kableExtra::column_spec(8, width='5em')

```


```{r, echo=FALSE}
Table
```


<!-- <p><embed src="https://www.datalimitedtoolkit.org/Case_Studies_Table/CaseStudies.html" width="1200" height="3000"></embed></p> -->

