---
date: "2021-01-22T11:35:01+06:00"
title: Populate the Stock Object
weight: 2
---

```{r, include=FALSE}
library(openMSE)
```


In the last section the `OMinit` function was to create the OM Excel and Rmarkdown files:

```{r, eval=FALSE}
OMinit('MyOM')
```

Then, once the OM Excel and Rmarkdown files were populated, the OM was imported from the spreadsheet with:

```{r, eval=FALSE}
OM <- XL2Data('MyOM')
```
and the Rmarkdown file was compiled into an [OM documentation report](6-document-om/).

In this section we describe how to populate the Stock object for a data-limited fishery. 

Rather than populate the stock parameters in an Excel spreadsheet and importing into R, in this example we will create the `Stock` object directly in the R script. Note that this is equivalent to entering the parameters in the corresponding rows in the OM Excel file and importing with `XL2OM`.

```{r}
Stock <- new('Stock')
slotNames(Stock)
```

### Meta-Data


### Mortality and Maximum Age

### Recruitment Parameters

### Growth

### Maturity

### Depletion

### Spatial & Movement


